---
title: "HW4 — My Assigned Pilot Dataset"
author: "Your Name"
format:
  html:
    embed-resources: true  # one self-contained .html file, nothing else to commit
editor: visual
---

## Setup

```{r}

```

## Read in your dataset

```{r}

```

## Clean your data

Your file has real issues in it — missing values, at least one implausible/extreme value, and at least one column with mixed text-and-number entries. Find them, decide what to do about each, and say briefly why.

```{r}

```

## Correlation

```{r}

```

## Interpretation

*A short paragraph: what does this correlation suggest about the relationship between sleep and physical activity in this sample? Anything else about your dataset worth mentioning?*

TODO: your interpretation here.

## Sources

*A sentence or two: what sources did you turn to for help on this homework? Sources can be other people, posts on the internet, software documentation, AI tools — or none at all. (Honest answers here never lower your grade; using help well is part of coding.)*

TODO: your answer here.

---

## PSY 0210 extension: data-cleaning memo

*(0110 students: optional/ungraded — feel free to attempt for practice.)*

*A bulleted log (roughly 5–10 bullets) of every cleaning decision you made above: what you found, what you did about it, and why — written so someone else could retrace and defend each choice.*

- TODO: your memo here.
