---
title: "HW6 — Simulate Your Pilot Design"
author: "Your Name"
format:
  html:
    embed-resources: true  # one self-contained .html file, nothing else to commit
editor: visual
---

## Setup

```{r}
library(tidyverse)
```

## Simulate your pilot design

Your own HW3 condition means as the centers; the class pooled between-subject SD (from class10) as the spread. Same mechanics as class10's guided build.

```{r}
# TODO: replace with your own HW3 means and the class pooled SD
set.seed(2026)
n_participants <- 20  # simulated people, not trials

congruent   <- rnorm(n_participants, mean = 600, sd = 90)
incongruent <- rnorm(n_participants, mean = 650, sd = 90)

sim_data <- tibble(
  participant = rep(1:n_participants, times = 2),
  condition   = rep(c("congruent", "incongruent"), each = n_participants),
  mean_rt     = c(congruent, incongruent)
)
```

## Save your simulated data

Simulated data is fine to commit — this isn't real pilot data.

```{r}
dir.create("data", showWarnings = FALSE)
write_csv(sim_data, "data/pilot_sim.csv")
```

## Wrangle

Same dplyr pattern as HW3, applied to your simulated data. Your final object **must be named `summary_table`**, with a mean-DV column whose name starts with `mean_`.

```{r}
summary_table <- sim_data |>
  group_by(condition) |>
  summarize(
    mean_rt = mean(mean_rt),
    n = n()
  )

summary_table
```

## Visualize

Your class08 figure code, adapted to the simulated table.

```{r}
# TODO: build your figure
```

## Sources

*A sentence or two: what sources did you turn to for help on this homework? Sources can be other people, posts on the internet, software documentation, AI tools — or none at all. (Honest answers here never lower your grade; using help well is part of coding.)*

TODO: your answer here.

---

## PSY 0210 extension: two sample sizes

*(0110 students: optional/ungraded — feel free to attempt for practice.)*

Re-run your simulation with a much larger N (e.g., 200), plot both versions with the same figure code, and answer below.

```{r}
# TODO (0210): the same simulation at a second sample size, plus its plot
```

*1–2 sentences: what changed between the two plots, and why?*

TODO: your answer here.
