---
title: "HW7 — Final Project Analysis"
author: "Your Name"
format:
  html:
    embed-resources: true  # one self-contained .html file, nothing else to commit
editor: visual
---

## Setup

```{r}
library(tidyverse)
```

## Simulate your design

No real participant data to match — pick plausible parameters for your own task and simulate from them, same `rnorm()` mechanics as class10 and HW6.

```{r}
# TODO: replace with your own design's parameters
set.seed(2026)
n <- 20  # per condition, must be >= 18 (the course's minimum-observations rule)

# TODO: adapt condition names and DV to your own task
condition_a <- rnorm(n, mean = 600, sd = 80)
condition_b <- rnorm(n, mean = 650, sd = 90)

simulated_data <- tibble(
  condition = rep(c("condition_a", "condition_b"), each = n),
  dv = c(condition_a, condition_b)
)
```

## Save your simulated data

Simulated data is fine to commit — this isn't real pilot data.

```{r}
dir.create("../data", showWarnings = FALSE)  # created in HW5; harmless if it already exists
write_csv(simulated_data, "../data/final_project_simulated.csv")
```

## Wrangle

Same dplyr pattern as HW3, applied to your simulated data. Your final object **must be named `summary_table`**.

```{r}
# TODO: adapt to your own column names — the mean-DV column's name must
# start with "mean_" (e.g. mean_rt, mean_acc) for the automated check
summary_table <- simulated_data |>
  group_by(condition) |>
  summarize(
    mean_rt = mean(dv, na.rm = TRUE),
    n = n()
  )

summary_table
```

## Visualize

Same ggplot2 pattern as class08.

```{r}
# TODO: build your figure
```

## Sources

*A sentence or two: what sources did you turn to for help on this homework? Sources can be other people, posts on the internet, software documentation, AI tools — or none at all. (Honest answers here never lower your grade; using help well is part of coding.)*

TODO: your answer here.

---

## PSY 0210 extension: the null twin

*(0110 students: optional/ungraded — feel free to attempt for practice.)*

Simulate your design again with the two condition means set **equal**, save it as a second CSV in the repo-root `data/` folder, and plot it with the same figure code as above.

```{r}
# TODO (0210): null simulation — same code as your simulation above,
# but with equal means; save to ../data/final_project_null.csv and plot
```

*1–2 sentences: what does the null version look like, and could you have told the two plots apart by eye?*

TODO: your answer here.
